Nonlinear methods to quantify Movement Variability in Human-Humanoid Interaction Activities

### 2020-12-17 docs/manuscript/main.tex
merge RPs figures into one

\subsection*{Recurrences Plots}
Using the average embedding parameters 
($\overline{m}_0=6$, $\overline{\tau}_0=8$) 
and an recurrence threshold of $\epsilon=1$.
As our interest is for dynamical transitions, 
there is little importance on the selection of $\epsilon$ which in this case
is 1. 
Recurrence Plots (RP) were computed for horizontal (figures~\ref{fig:rp_aH}) and 
vertical (figures~\ref{fig:rp_aV}) arm movements.
%%---------------------------------(FIGURE)-------------------------------------
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{figures/rps/pdf/rp_aH}
\caption{
	{\bf RPs for horizontal arm movements.}	
	Recurrence plots were computed with 
	embedding parameters 
	$\overline{m}_0=6$, $\overline{\tau}_0=8$, and $\epsilon=1$.
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig:rp_aH}
\end{figure}
%%---------------------------------(FIGURE)------------------------------------
%%---------------------------------(FIGURE)-------------------------------------
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{figures/rps/pdf/rp_aV}
\caption{
	{\bf RPs for vertical arm movements.}	
	Recurrence plots were computed with 
	$\overline{m}_0=6$, $\overline{\tau}_0=8$, and $\epsilon=1$.
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig:rp_aV}
\end{figure}
%%---------------------------------(FIGURE)------------------------------------

>>>>

\subsection*{Recurrences Plots}
Using the average embedding parameters 
($\overline{m}_0=6$, $\overline{\tau}_0=8$) 
and an recurrence threshold of $\epsilon=1$.
As our interest is for dynamical transitions, 
there is little importance on the selection of $\epsilon$ which in this case
is 1. 
Recurrence Plots (RP) were computed for horizontal (figures~\ref{fig:rps}(A)) and 
vertical (figures~\ref{fig:rps}(B)) arm movements.
%%---------------------------------(FIGURE)-------------------------------------
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{figures/rps/versions/drawing-v00.pdf}
\caption{
	{\bf RPs for horizontal (A) and vertical (B) arm movements.}	
	Recurrence plots were computed with 
	embedding parameters 
	$\overline{m}_0=6$, $\overline{\tau}_0=8$, and $\epsilon=1$.
	Code and data to reproduce the figure is available in \cite{srep2020}.
        }
    \label{fig:rps}
\end{figure}
%%---------------------------------(FIGURE)------------------------------------
